Hydra Battles and Cie

### 2021-08-30 doc/part-hydras.tex
small issue in snippet Omega_Small/mGeb
[doc] Add an \inputsnippets command and demo it in Schutte/AP.v

The relation between \texttt{one\_step} and the rules of hydra battle is asserted by the following lemma.

@@

\vspace{4pt}
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#Hvariant}{Hydra.Hydra\_Definitions}}

@@

\input{movies/snippets/Omega_Small/mGeb}

\input{movies/snippets/Omega_Small/omegaSmallz}

@@

\input{movies/snippets/ON_Generic/ONDefs}

@@

\input{movies/snippets/ON_Omega/OmegaDef}

@@

@@

\input{movies/snippets/AP/APOne}

>>>>

The relation between \texttt{one\_step} and the rules of hydra battles is asserted by the following lemma.

@@

\vspace{4pt}
\noindent

\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#Hvariant}{Hydra.Hydra\_Definitions}}

@@

\inputsnippets{Omega_Small/mGeb, omega_Small/mGez,
  Omega_Small/omegaSmallz}

@@

\inputsnippets{ON_Generic/ONDefsa, ON_Generic/ONDefsb}

@@

\inputsnippets{ON_Omega/OmegaDefa, ON_Omega/OmegaDefb}

@@

\pagebreak

@@

\inputsnippets{AP/APOne,AP/APOne_least_AP,AP/APOne_AP_omega,AP/APOne_omega_second_AP}
